---
title: "Book Sales Analysis"
author: "Kathan Vakharia"
date: "24/07/2020"
output: html_document
---
## Introduction
* This project demonstrates a simple data analyses work flow on a book 
sales [data set](https://data.world/dataquest/book-reviews).
* The main objective of this analysis is to find out which book is most famous.

### Importing the data-set
```{r importing-data, message=FALSE}
library(tidyverse)
book_reviews = read_csv("../datasets/book_reviews.csv")
```

### Getting Insights from Data-Set
```{r Getting used to dataset}
#getting over-view 
glimpse(book_reviews) 
column_vector <- colnames(book_reviews)
print(column_vector)
print(book_reviews)
```

```{r}
#another way to inspect data type of columns
for(column in column_vector){
  print(typeof(book_reviews[[column]]))
}
```
```{r}
#finding unique values for categorical variables
#This helps to check if NA values are present
review_values <- unique(book_reviews$review)
states_values <- unique(book_reviews$state)
prices_values <- unique(book_reviews$price)
list("unique_reviews"=review_values, "unique_states" = states_values,
     "unique_prices"=prices_values)
```
```{r}
#min max price
min_price <- min(book_reviews$price)
max_price <- max(book_reviews$price)

print(c("min_price"=min_price, "max_price" = max_price))

```

### Dealing will NA values
By examining unique values of reviews, we can see there are "NA"(Not Available) values present for some rows.So we are gonna remove it
```{r}
#removing rows with NA values
book_reviews_cleaned <- book_reviews %>%
  filter(!is.na(review))

#comparing the old and cleaned data set
list("old_dimensions"=dim(book_reviews), "new_dimensions"=dim(book_reviews_cleaned))

```
### Removing inconsistencies in State Names
As some states' name are full names and some are shortened versions,for consistency, we converted every state name to shortened version.
```{r}
book_reviews_cleaned <- book_reviews_cleaned %>%
  mutate(state = case_when(
    state == "California" ~ "CA",
    state == "New York" ~ "NY",
    state == "Texas" ~ "TX",
    state == "Florida" ~ "FL",
    TRUE ~ state
  ))
```
### Converting Reviews into numbers
As reviews as strings won't give us much context, it is better we convert them into numbers for example, Excellent = 5,..., Poor = 1
```{r}
book_reviews_cleaned <- book_reviews_cleaned %>%
  mutate(review_num = case_when(
    review == "Poor" ~ 1,
    review == "Fair" ~ 2,
    review == "Good" ~ 3,
    review == "Great" ~ 4,
    review == "Excellent" ~ 5
  ))
```

#### Marking some reviews as HIGH
Just for sake to see high rated books, creating a Logical column,which will
be TRUE if review_num >= 4 and FALSE otherwise.

```{r}
book_reviews_cleaned <- book_reviews_cleaned %>%
  mutate(is_high_review = case_when(
    review_num > 3 ~ TRUE,
    TRUE ~ FALSE
  ))
```

### Finding the most profitable book
There are two parameters we can judge which book is profitable,

 1. Which was sold most.
 2. Which generated maximum revenue 
 *  Both metrics are plausible

#### Making potent columns

1. copies_sold = contains number of copies sold
2. revenue_generated = contains total revenue generated

```{r}
book_review_summarised <- book_reviews_cleaned %>%
  group_by(book) %>%
  summarise(
    copies_sold = length(book),
    revenue_generated = sum(price),
    .groups = 'drop'
  )
```

### Sorting by copies_sold
```{r}
books_sold_most <- book_review_summarised %>% arrange(desc(copies_sold))
```

```{r echo=FALSE}
print(books_sold_most)
```
So, we conclude that <strong> _`r books_sold_most$book[1]`_</strong>   was sold maximum number of times.

### Sorting by revenue_generated
```{r}
books_revenue_most <- book_review_summarised %>% arrange(desc(revenue_generated))
```
So, we conclude that  <b>_`r books_revenue_most$book[1]`_</b>  generated maximum revenue.

```{r echo=FALSE}
print(books_revenue_most )
```

## Conclusion:
In the end, we conclude that depending on different parameters famous books are different. Although there's not much difference between the most famous and rest

* Limitation : We skipped the rows with NA values which might have some useful data






















